Precise Weed and Maize classification through Convolutional Neuronal Networks

### 2017-07-20 PaperBCJ.tex
Auto stash before merge of "master" and "origin/master"
Table of fps

\begin{table}[h!]
\centering
\begin{tabular}[c c c c]{|p{2.2 cm}|p{1.1cm}|p{1.1cm}|p{2.4cm}|} 
 \hline
 \textbf{Hardware } & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification/image}\\ 
 \hline 
 GPU & 89.11\% & 92.08\% & 1.58 ms \\ [0.95ex]
 \hline
 CPU & 89.11\% & 92. 08\% & 10.92 ms \\ [0.95ex]
 \hline
 CPU(Raspberry Pi) & 92.08\% & 87.13\% & 150.8 ms \\ [0.95ex]
 \hline
\end{tabular}
\caption{Test of cNET 16 filters with optimized software}
\label{table:5}
\end{table}

@@

>>>>

\begin{table}[h!]
\centering
\begin{tabular}[c c c c]{|p{2.2 cm}|p{1.1cm}|p{1.1cm}|p{2.4cm}|} 
 \hline
 \textbf{Hardware } & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification/image}\\ 
 \hline 
 GPU & 89.11\% & 92.08\% & 1.58 ms \\ [0.95ex]
 \hline
 CPU & 89.11\% & 92.08\% & 10.92 ms \\ [0.95ex]
 \hline
 CPU(Raspberry Pi) & 89.11\% & 92.08\% & 150.8 ms \\ [0.95ex]
 \hline
\end{tabular}
\caption{Test of cNET 16 filters with optimized software}
\label{table:5}
\end{table}

@@

\begin{comment}	
Ahora para comparar todos estos resultados tomando en cuenta que una imagen capturada por la camara a una altura de 1,5 m puede enfocar un aproximado de 6 plantas de maiz, y segun la cantidad de mala hierba, se considerara un promedio de 12 plantas, dando un total de 18 plantas aproximadamente. Con esto se analiza cuantos frames por segundo seria lo adecuado para la adquisicion de imagenes.
\end{comment}	
Now to compare all these results taking into account that an image captured by the camera at a height of 1.5 m can focus an approximate 6 plants of maize, and according to the amount of weed, an average of 12 plants, Giving a total of about 18 plants. This analyzes how many frames per second would be appropriate for the acquisition of images.
\begin{table}[h!]
\centering
\begin{tabular}[c c c c]{|p{1.1 cm}|p{1.7cm}|p{1.7cm}|p{2.0cm}|} 
 \hline
 \textbf{Parameter} &\textbf{GPU(Without Threading) } & \textbf{CPU with Threading} & \textbf{RaspBerry Pi 3 with Threading} \\ 
 \hline 
 Time(s) & 0.0171 & 0.196 & 7.714  \\ [0.95ex]
 \hline
 FPS & 58.47  & 5.08 & 0.36  \\ [0.95ex]
 \hline
\end{tabular}
\caption{Test of a complete image and the frames per second}
\label{table:5}
\end{table}
